Supporting Information:\n prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-10-30 inst/MyArticle/prolfqua_supplement.Rmd
edits

ISMpeptide <- dplyr::bind_rows(mrob,proda,prolfqua, msstats) |> dplyr::filter(contrast == "all")
ISMpeptide$contrast <- NULL
ISMpeptide <-dplyr::relocate(ISMpeptide , package, .before="AUC") |> dplyr::arrange(what)
ISMpeptide$what[ISMpeptide$what=="statistic"] <- "t_statistic"
ISMpeptide |> 
  knitr::kable(digits = 1, caption = "Results of the DEA beanchmark for IonStar/MaxQuant/peptide.txt")
```

@@

all$contrast <- NULL
all |> dplyr::relocate(package, .before = "AUC") |> dplyr::arrange(what) |> 
  knitr::kable(digits = 1, caption = "Results of the DEA beanchmark for CPTAC/MaxQuant/peptide.txt")

@@

ISFPprot <- dplyr::bind_rows(proda, prolfqua)
ISFPprot$what[ISFPprot$what == "statistic"] <- "t_statistic"
ISFPprot$what[ISFPprot$what == "scaled.pval"] <- "scaled.p.value"
ISFPprot <- ISFPprot |> 
  dplyr::filter(contrast == "all")
ISFPprot$contrast <- NULL
ISFPprot |> dplyr::relocate(package, .before = "AUC") |> dplyr::arrange(what) |>
  knitr::kable(digits = 1, caption = "Results of the DEA beanchmark for IonStar/FragPipeV14/MSstats.tsv")

@@

(ref:plotFragPipebarplot) Barplot showing the partial area under the ROC at 0.1 FDR, for diff - difference among groups, scaled.p.value and t_statistic. These results where obtained when using FragPipeV14 combined_protein.txt as input.

@@

(ref:isFPbarplot)

@@

ISFPmsstats$what[ISFPmsstats$what == "logFC"] <- "diff"
ISFPmsstats$what[ISFPmsstats$what == "log2FC"] <- "diff"
ISFPmsstats$what[ISFPmsstats$what == "t"] <- "t_statistic"
ISFPmsstats$what[ISFPmsstats$what == "Tvalue"] <- "t_statistic"
ISFPmsstats$what |> unique()

@@

ISFPmsstats |> 
  knitr::kable(digits = 1, caption = "Results of the DEA beanchmark for IonStar/FragPipeV14/MSstats.tsv")

@@

# Comparing DEA results for MaxQuant and FragPipe

@@

ggplot2::ggplot(tmp, aes(x=package, y = pAUC_10, fill = software))+
  ggplot2::geom_bar(stat = "identity",position = "dodge") +
  scale_fill_grey() +
  ggplot2::facet_wrap(~what)  + 
  ggplot2::theme_minimal() + 
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = -90, vjust = 0.5)) +
  ggplot2::xlab("")

@@

```{r contrcoefficient}
knitr::kable(mC, caption = "Weights $c$ for each of the contrasts (rows) which will be applied to the model parameter (columns).",format = "latex")
```

>>>>

ISMpeptide <- dplyr::bind_rows(mrob,proda,prolfqua, msstats) |> dplyr::filter(contrast == "all")
ISMpeptide$contrast <- NULL
ISMpeptide <-dplyr::relocate(ISMpeptide , package, .before="AUC") |> dplyr::arrange(what)
ISMpeptide$what[ISMpeptide$what == "statistic"] <- "t_statistic"
ISMpeptide |> 
  knitr::kable(
    digits = 1, 
    caption = "Results of the DEA beanchmark for IonStar/MaxQuant/peptide.txt",
    format = "latex")
```

@@

all$contrast <- NULL
all |> dplyr::relocate(package, .before = "AUC") |> dplyr::arrange(what) |> 
  knitr::kable(digits = 1,
               caption = "Results of the DEA beanchmark for CPTAC/MaxQuant/peptide.txt", 
               format = "latex")

@@

ISFPprot <- dplyr::bind_rows(proda, prolfqua)
ISFPprot$what[ISFPprot$what == "statistic"] <- "t_statistic"
ISFPprot$what[ISFPprot$what == "scaled.pval"] <- "scaled.p.value"
ISFPprot <- ISFPprot |> 
  dplyr::filter(contrast == "all")
ISFPprot$contrast <- NULL
ISFPprot |> dplyr::relocate(package, .before = "AUC") |> dplyr::arrange(what) |>
  knitr::kable(digits = 1,
               caption = "Results of the DEA beanchmark for IonStar/FragPipeV14/MSstats.tsv",
               format = "latex")

@@

(ref:plotFragPipebarplot) Barplot showing the partial area under the ROC at $0.1$ FDR ($pAUC_{10}$), for diff - difference among groups, scaled.p.value and t_statistic. These results where obtained when using IonStar/FragPipeV14/combined_protein.txt as input.

@@

(ref:isFPbarplot) Barplot showing the partial area under the ROC at 0.1 FDR ($pAUC_{10}$), for diff - difference among groups, scaled.p.value and t_statistic. These results where obtained when using IonStar/FragPipeV14/MSstats.tsv as input.

@@

ISFPmsstats$what[ISFPmsstats$what == "logFC"] <- "diff"
ISFPmsstats$what[ISFPmsstats$what == "log2FC"] <- "diff"
ISFPmsstats$what[ISFPmsstats$what == "t"] <- "t_statistic"
ISFPmsstats$what[ISFPmsstats$what == "Tvalue"] <- "t_statistic"

@@

ISFPmsstats |> 
  knitr::kable(
    digits = 1,
    caption = "Results of the DEA beanchmark for IonStar/FragPipeV14/MSstats.tsv",
    format = "latex")

@@

# Comparing DEA results for *MaxQuant* and *FragPipe*

@@

ggplot2::ggplot(tmp, ggplot2::aes(x=package, y = pAUC_10, fill = software))+
  ggplot2::geom_bar(stat = "identity",position = "dodge") +
  ggplot2::scale_fill_grey() +
  ggplot2::facet_wrap(~what)  + 
  ggplot2::theme_minimal() + 
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = -90, vjust = 0.5)) +
  ggplot2::xlab("")

@@

```{r contrcoefficient}
cap = "Weights $c$ for each of the contrasts (rows) which will be applied to the model parameter (columns)."
knitr::kable(mC, caption = cap,format = "latex")
```
